\documentclass[11pt,letterpaper,sans]{moderncv}

\usepackage[scale=0.82]{geometry}
\usepackage{textcomp}

\moderncvstyle{banking} 
\moderncvcolor{black}
\nopagenumbers{} 
\renewcommand*{\addressfont}{\small\mdseries}

\name{Sarah J.}{Elliott}
\address{1800 Bryant Street Apt. 305}{San Francisco, CA 94110}
\phone[mobile]{+1~(406)~672~8090}
\email{sarahjeanelliott77@gmail.com}
\social[twitter]{sarahelliott77}
\quote{Offense beats defense.}

\begin{document}
\makecvtitle
\vspace*{-10mm}

\section{Summary}
\small{A seasoned and fearless public relations and policy strategist at the
intersection of politics, policy, and legislative action. My work is
featured in the New York Times, Washington Post, POLITICO, The Colbert
Report, Charlie Rose, Bill Maher, 60 Minutes, and others.}

\section{Experience}
\cventry{11/2015--present}{Senior Consultant, Corporate Communications}{Solazyme, Inc.}{
San Francisco, CA}{}{
I am a senior communications consulting executive with responsibility
for top-to-bottom messaging and launch strategy across many product
verticals.
\begin{itemize}
\item Conceived and authored all messaging and digital and print collateral
 for product launch in new vertical.
\item Created presentation materials for c-suite executives for product announcement.
\item Provided day-to-day media and messaging support for existing product lines.
\end{itemize}
}

\cventry{11/2015--present}{Senior Advisor}{Squared Communications}{San Francisco, CA}{}{
I provide ongoing input on strategy and messaging for critical accounts.
}

\cventry{1/2013--12/2015}{Senior Vice President, Head of West Coast Operations}
{Squared Communications}{San Francisco, CA}{}{
I ran West Coast operations and managed multiple key accounts,
specializing in patent reform, data privacy, and health care.
\begin{itemize}
\item Developed and executed earned and paid media and policy strategies.
\item Clients included Google, Application Developers Alliance,
Vulcan Productions, Main Street Patent Coalition, and Green Tech Action
Fund.
\end{itemize}
}

\cventry{11/2004--11/2013}{Communications Director}{Montana Governor Brian Schweitzer}{}{}
{I was appointed to oversee all media operations for Governor Schweitzer
and the executive branch including the budget, speech writing, and major
media events.
\begin{itemize}
\item Directed day-to-day press operations, crisis communications and advised
the Governor on public facing decisions.
\item Secured national media appearances including: 60 Minutes, The Late Show with David Letterman, NBC Nightly News, The Colbert Report, The Rachel Maddow Show, Hardball, Morning Joe, Fox News, Fox and Friends, and many others.
\item Communications for Schweitzer`s 2008 re-election campaign, winning with more than 65\% of the vote. Lead writer of 2008 and 2012 Democratic National Convention speeches.
\end{itemize}
}


\cventry{11/2003--11/2004}{Communications Director}{Montana Auditor John Morrison}{}{}{
I directed communications for the Office of Insurance and Securities and
a successful re-election campaign in 2004, winning with more than 55\%
of the vote.
}

\cventry{1/2003--12/2003}{Scheduler/Press Office}{Denver Mayor John Hickenlooper}{}{}{}

\cventry{1/2000--1/2003}{Assignment Editor, Reporter}{KULR 8}{}{}{}

\section{Education}
\cventry{1996--2001}{Organizational Communications}{Montana State University - Billings}{
Billings, MT}
{}{}

\end{document}

